Capstone Movielens Report

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Value section): print_log2, put_log2, print_log3, put_log3, print_log4, put_log4.

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log2](#func.get_log2) function described above.

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log2](#func.get_log2) function described above.
:::

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log3](#func.get_log3) function described above.

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log3](#func.get_log3) function described above.
:::

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log4](#func.get_log4) function described above.

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log4](#func.get_log4) function described above.
:::

>>>>

A glue object, returned by the internally called function [get_log2](#func.get_log2) described above.

@@

A glue object, returned by the internally called function [get_log2](#func.get_log2) described above.
:::

@@

A glue object, returned by the internally called function [get_log3](#func.get_log3) described above.

@@

A glue object, returned by the internally called function [get_log3](#func.get_log3) described above.

@@

A glue object, returned by the internally called function [get_log4](#func.get_log4) described above.

@@

A glue object, returned by the internally called function [get_log4](#func.get_log4) described above.
:::
